Refinements for open automata

### 2021-12-17 2021-Refinement/paper/refinementarticle.tex
proof thm2 progress

\TODO{peut etre echanger c et p? ou c devient p et p devient? }
\begin{definition}[Composition of open automata]
The composition of \(A_c = \OAg[c]\) in the hole \(k \in J_p\) of \(A_p = \OAg[p]\) is the OA defined as follows:
\[A_p\subst{A_c}{k} ::=  \OA{S_p \times S_c}{\mpar{s_{0p}, s_{0c}}}{V_p \uplus V_c}{\sigma_{0p} \uplus \sigma_{0c}}{J_c \uplus J_p \setminus \mbrc{k}}{T} \] \text{with }

@@

\section{Proof of Context Refinement}
Let us denote by $A_{13}$ (resp. $A_{23}$) the open automaton resulting from $A_1\subst{A_3}{k}$ ($A_2\subst{A_3}{k}$),  to prove the theorem it sufficient to prove that there exists a relation between states of the two open automata that satisfies the conditions of the Definition \ref{Def:OA-Refinement}. Let $R$ be the refinement relation relating states of $A_1$ and $A_2$.\\
Let us define $R'$ the relation:
\[R' \mpar{\mpar{s_{13}, s'_{13}}, \mpar{s_{23}, s_{23}'}} = \choice{R\mpar{s_{13}, s_{23}} \wedge \reach{A_{13}}\mpar{s_{13},s_{13}'} \wedge\!\!\!\! \bigwedge_\subbox{\begin{array}{c}
v\in \fvars{s'_{13}}\\
v\in V_3
\end{array}}\!\!\! \sigma_{13}(v)=\sigma_{23}(v) & \text{ if } s'_{13} = s'_{23} \\ \bot & \text{otherwise}} \]
We want to prove that $\mpar{R, H\cup J_3 \setminus\{k\}}$ is a hole-tracking simulation of $A_{13}$ and $A_{23}$.
\begin{enumerate}
\item By using the fact $R$ relates initial configurations of  $A_1$ and $A_2$, initial state is reachable and renaming $\sigma_{03}$ by  $\sigma_{013}$ and  $\sigma_{023}$ we need to prove:
\[\sigma_{013} \uplus \sigma_{023} \vdash R'\mpar{s_{013}, s_{023}}\]

We have by hypothesis:
\begin{align*}
& \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}} \wedge 
\mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}}\\
\iff & R\mpar{s_{01}, s_{02}}\psubst{ \sigma_{01} \uplus \sigma_{02}} \wedge \reach{A_{13}}\mpar{s_{013}} \psubst{\sigma_{013}} \wedge \bigwedge_\subbox{\begin{array}{c}
v\in V_3
\end{array}} \sigma_{03}(v)=\sigma_{03}(v)\\
\iff & R\mpar{s_{01}, s_{02}}\psubst{ \sigma_{01} \uplus \sigma_{02}} \wedge \reach{A_{13}}\mpar{s_{013}} \psubst{\sigma_{013}} \wedge \bigwedge_\subbox{\begin{array}{c}
v\in V_3
\end{array}} \sigma_{013}(v)=\sigma_{023}(v)
\end{align*}

>>>>

\TODO{peut etre echanger c et p? ou c devient p et p devient? }
\begin{definition}[Composition of open automata] \label{Def:CompOA}
The composition of \(A_c = \OAg[c]\) in the hole \(k \in J_p\) of \(A_p = \OAg[p]\) is the OA defined as follows:
\[A_p\subst{A_c}{k} ::=  \OA{S_p \times S_c}{\mpar{s_{0p}, s_{0c}}}{V_p \uplus V_c}{\sigma_{0p} \uplus \sigma_{0c}}{J_c \uplus J_p \setminus \mbrc{k}}{T} \] \text{with }

@@

\section{Proof of Context Refinement}
Let us denote by $A_{13}$ (resp. $A_{23}$) the open automaton resulting from $A_1\subst{A_3}{k}$ ($A_2\subst{A_3}{k}$),  to prove the theorem it sufficient to prove that there exists a relation between states of the two open automata that satisfies the conditions of the Definition \ref{Def:OA-Refinement}. Let $R$ be the refinement relation relating states of $A_1$ and $A_2$.\\
Let us consider any two states $s_{13} = \mpar{s_1,s_3}$ and $s_{23} = \mpar{s_2,s_3'}$ we define a relation $R'$ relating states of $A_{13}$ and $A_{23}$ as follows:
\[R' \mpar{s_{13}, s_{23}} = \choice{R\mpar{s_{1}, s_{2}} \wedge \reach{A_{13}}\mpar{s_{13}} \wedge\!\!\!\! \bigwedge_\subbox{v\in \fvars{s_{3}}
}\!\!\! \sigma_{13}(v)=\sigma_{23}(v) & \text{ if } s_{3} = s'_{3} \\ \bot & \text{otherwise}} \]
We want to prove that $\mpar{R', H\cup J_3 \setminus\{k\}}$ is a hole-tracking simulation of $A_{13}$ and $A_{23}$.
\begin{enumerate}
\item By using the fact $R$ relates initial configurations of  $A_1$ and $A_2$, initial states are reachable and by renaming $\sigma_{03}$ by  $\sigma_{013}$ and  $\sigma_{023}$ we need to prove:
\[\sigma_{013} \uplus \sigma_{023} \vdash R'\mpar{s_{013}, s_{023}}\]

We have by hypothesis:
\begin{align*}
& \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}} \wedge 
\mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}}\\
\iff & R\mpar{s_{01}, s_{02}}\psubst{ \sigma_{01} \uplus \sigma_{02}} \wedge \reach{A_{13}}\mpar{s_{013}} \psubst{\sigma_{013}} \wedge \bigwedge_\subbox{v\in V_3} \sigma_{03}(v)=\sigma_{03}(v)\\
\iff & R\mpar{s_{01}, s_{02}}\psubst{ \sigma_{01} \uplus \sigma_{02}} \wedge \reach{A_{13}}\mpar{s_{013}} \psubst{\sigma_{013}} \wedge \bigwedge_\subbox{v\in V_3} \sigma_{013}(v)=\sigma_{023}(v)\\
\iff & R\mpar{s_{01}, s_{02}} \wedge \reach{A_{13}}\mpar{s_{013}}  \wedge \bigwedge_\subbox{v\in V_3} \sigma_{013}(v)=\sigma_{023}(v) \psubst{ \sigma_{01} \uplus \sigma_{02} \uplus \sigma_{013} \uplus \sigma_{023}}
\end{align*}
\item We need to prove for any OT $t_{13}$ originating from $s_{13}$:
\begin{align*}
		&  \OTx{13}{}{13}{13} \in \fOT{s_{13}}
\end{align*}		
there exist an indexed family $t_{23x}$ of OTs originating from $s_{23}$: 
\begin{align*}
		&  \mpar{\OTx{23}{x}{23x}{23x} \in \fOT{s_{23}}}^{x \in X}
\end{align*}	
\begin{align*}		
		& \quad \mpar{\forall x \in X, J'_{23x} \cap H = J'_{13} \cap H} \nwedge\\
		&  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash R\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H} \beta_{13j} = \beta_{23xj} \\[12pt]
			\nwedge g_{23x} \wedge R\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
		\end{array}} 
	\end{align*}
According to Definition \ref{Def:CompOA}, we know that $t_{13}$ is built by:
 \[  \choice{
	\OTx{1}{}{1}{1} \wedge  \OTx{3}{}{3}{3}
	& \text{if } k \in J'_{1} \\
	\OTx{1}{}{1}{1}	 & \text{otherwise}
	} \]

By hypothesis, we have for any open transition $t_1$ in $T_1$  originating from $s_1$:
\begin{align*}
\OTx{1}{}{1}{1} \in \fOT{s_1}
\end{align*}
there exist an indexed family of OTs originating from $s_{2}$: 
\begin{align*}
\mpar{\OTx{2}{x}{2x}{2x} \in \fOT{s_{2}}}^{x \in X} 
\end{align*}
such that $\forall x \in X, J'_{2x} \cap H = J'_1 \cap H$ and
\begin{multline*}
%\everymath{\displaystyle}
V_1 \uplus V_2 \uplus \fvars{t_1} \vdash\\ \mpar{R\mpar{s_1, s_{2}} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj} \nwedge\\
			 g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
		\end{array}}} 
\end{multline*}
